Thermodynamic characterization of the adsorption of amino acids onto pristine graphene and graphene oxide

### 2021-12-13 paper/main.tex
Automated copying of data and making of some figures

@@

>>>>

\begin{figure}[htbp]
\centerline{\includegraphics[width=\columnwidth]{/home/mbarria/Dropbox/Papers/graphene_adsorption_paper/figures/Pristine_System.png}}
\caption[]{\label{fig:system-pristine} Example of simulated pristine
  graphene systems. An amino acid (in this case Phenylalanine) above a
  graphene layer (in gray) inside a periodic water box.}
\end{figure}

\begin{figure}[htbp]
\centerline{\includegraphics[width=\columnwidth]{/home/mbarria/Dropbox/Papers/graphene_adsorption_paper/figures/Oxidized_System_and_Unit.png}}
\caption[]{\label{fig:system-oxidized} a) Example of simulated oxidized
  graphene systems. An amino acid (in this case Phenylalanine) above a
  graphene layer (C in gray, O in red, H in white) inside a periodic
  water box. b) Segment of the oxidized graphene layer depicting the
  oxidation pattern. (C in gray, O in red, H in white)}
\end{figure}

@@

\begin{figure*}[htbp]
\centerline{\includegraphics[width=\textwidth]{/home/mbarria/Dropbox/Papers/graphene_adsorption_paper/figures/Differences_by_names_and_weight_25o.png}}
\caption[]{\label{fig:differences} Differences of adsorption over an
  oxidized graphene layer for free energies ($\Delta A_{ads}$),
  energies ($\Delta E_{ads}$) and entropies ($T \Delta S_{ads}$) for
  select amino acids. All values are relative to Glycine's, which is
  set to 0. Top row (a, c, and e): $\Delta A_{ads}$,
  $\Delta E_{ads}$, and $T \Delta S_{ads}$, arranged by amino acid
  classification on the basis of side-chain interactions. Amino acids
  are labeled on the x-axis by their three letter code. Bottom row (b,
  d, and f): $\Delta A_{ads}$, $\Delta E_{ads}$, and
  $T \Delta S_{ads}$, as a function of molecular weight of the amino
  acid. Amino acids are labeled by their markers with their one letter
  code. In all cases amino acids are in a neutral state unless marked
  with a positive ($+$) or negative ($-$) sign.}
